\documentclass[11pt]{scrartcl}
\usepackage{atbegshi,picture}
\usepackage{lipsum}

\AtBeginShipout{\AtBeginShipoutUpperLeft{%
  \put(\dimexpr\paperwidth-1cm\relax,-1.5cm){\makebox[0pt][r]{Master on Free Software 2012/2013}}%
}}

\title{\textbf{FLOSS Software Engineering}}
\subtitle{FLOSS developers characterisation}

\author{Felipe Ortega\\
		Ricardo Grac\'ia Fern\'andez}
\date{\today}
\begin{document}

\maketitle


There seems to be a predefined stereotype of what a FLOSS developer should be, look like and how she should act. In this session we will try to find out about FLOSS developers. We will look at the people that is behind the FLOSS phenomena: their motivations, their behaviour and their circumstances.

\section*{Debate}

The following statements may be true or false... or just inexact... or even made up. State an opinion on everyone of them and debate it in the classroom.

\begin{enumerate}

	\item Gender in FLOSS
	\begin{enumerate}
		\item There is as many women involved in FLOSS as men

		\textbf{False}, in the charts only few women work as FLOSS.
		\item Women in FLOSS carry out different tasks than men
		
		\textbf{False}, in development all the people develops.
		\item There is a deliberated discrimination against women in FLOSS
		
		\textbf{False}, it can't be because there aren't enough women to do it (joke answer).
	\end{enumerate}

	\item Age of the developers
	\begin{enumerate}
		\item Most FLOSS developers have no experience and are quite young
		
		\textbf{True-False}, because the age of FLOSS developers range is young but the greatest number has more experience after \textbf{n} years of development.
		\item There is little chance to become a FLOSS developer if you are over 40 years old
		
		\textbf{False}, but not at all because the age range in charts (in that moment in time) is younger and less people enter as FLOSS developer at 40 years but is lesser if you are over 50.
		\item The previous statement is true now but will not be in 40 years time
		
		\textbf{True}, using last explanation with 50 years sample.
	\end{enumerate}

	\item Relationship status of the developers (Bonus this year)
	\begin{enumerate}
		\item Most FLOSS developers are single and do not have a girlfriend
		
		\textbf{True very true} LOL.
	\end{enumerate}

	\item Educational Background of FLOSS Developers
	\begin{enumerate}
		\item Most FLOSS developers have a masters degree or PhD
		
		\textbf{False}, because most of FLOSS Developers are around University, titles, coursing a degree but not only with a master or PhD.
		\item There is no way you can become a FLOSS developer if you did not attend a university
		
		\textbf{False}, because all you need to start is your aim to do it, it's true that in university you have more conscience and are closer to FLOSS but is not necessary.
		\item FLOSS developers are usually self-taught
		
		\textbf{True-False}, because you need this ability but not only to become a FLOSS its a way to raise.
	\end{enumerate}

	\item Professional Background of FLOSS Developers
	\begin{enumerate}
		\item FLOSS developers work in non-IT-related jobs and write FLOSS as a hobby
		
		\textbf{False-True}, most of FLOSS developers work in IT-related job and write FLOSS as a \textbf{hobby}. I like this word for describe FLOSS developers motivation.
		\item FLOSS developers are executives of IT companies that have much more spare time and instead of playing golf, they write FLOSS
		
		\textbf{False} the same sentence answers the question.
		\item About one out of two FLOSS developers works in an university
		
		\textbf{False}, doesn't that FLOSS developer works in an university, I think they are related to university activities.
		\item Almost three out of a hundred FLOSS developers work in something not related to IT
		
		\textbf{True}, it's a percentile for this kind of FLOSS developers that are not related to IT.
	\end{enumerate}

	\item Time devoted to libre software projects
	\begin{enumerate}
		\item Most FLOSS developers spend their evenings (2 hours per night ~ 12 hours per week) writing code
		
		\textbf{True}, it's over 35\% people that is involved in FLOSS developments.
		\item Some FLOSS developers spend even more than 40 hours per week writing code
		
		\textbf{True}, if some could be a 15\%.
		\item FLOSS developers spend as much time writing code as anyone would spend in a hobby
		
		\textbf{True-False}, is not a competition between hobbies because fi it is, it stops being a hobby.
	\end{enumerate}

	\item Time devoted to libre software projects compared to proprietary software
	\begin{enumerate}
		\item All FLOSS developers only write FLOSS
		
		\textbf{False}, the word only defines the false answer.
		\item Those who spend the most time coding FLOSS are the ones that spend the most time coding proprietary software
		
		\textbf{False}, it has no sense 'the more you spend coding proprietary software the more time you spend coding FLOSS'.
		\item Most of FLOSS developers spend as much time coding FLOSS as coding proprietary software
		
		\textbf{False}, Nowadays it's a deprecated statement because a lot of companies write FLOSS code and it has not a direct or indirect relation.
	\end{enumerate}

	\item Take a break and try to write down the names of 5 FLOSS developers without
	searching in the Internet
	\begin{enumerate}
		\item Miguel DEA Icaza
		\item Micael Gallego
		\item Ben Alex
		\item Linus Torvalds
		\item 
	\end{enumerate}
	
	\item Motivations for developers to join and stay in the FLOSS community
	\begin{enumerate}
		\item Most developers are into this for the money
		
		\textbf{False}
		\item Some of them do not like that some large software are so powerful
		
		\textbf{True-False}, the competitive even the jealousy could be agree with this statement to fork a specific project.
		\item Most of them join the community to share their skills, just because they know that may be helpful
		
		\textbf{True}
		\item Most of them join to learn new skills
		
		\textbf{True}
		\item Some of them are into this looking for a girlfriend
		
		\textbf{Absolutely True}
	\end{enumerate}

	\item Earning money with FLOSS development
	\begin{enumerate}
		\item FLOSS developers do not get paid for their efforts
		
		\textbf{False-True}, because you could be get paid in some scenarios or never.
		\item Almost one out of two FLOSS developer does not earn a single cent with FLOSS
		
		\textbf{True} as Monetary rewards from developing FLOSS chart shows.
		\item Some of them think that FLOSS has helped them indirectly to earn money in non-FLOSS related jobs
		
		\textbf{False} because is only a 5\% that thinks that as the chart shows.
	\end{enumerate}

	\item Free Software vs. Open Source alignment
	\begin{enumerate}
		\item Almost half of the developers believe that the Free Software community is essentially the same thing as the Open Source Community
		
		\textbf{True} representing the 48,0\% of FLOSS developers.
		\item Many FLOSS developers do not really care whether they fall into the Free Software community or the Open Source Community neither think there is a major difference
		
		\textbf{True} a 19,4\% could be many.
	\end{enumerate}

	\item Localisation of FLOSS Developers
	\begin{enumerate}
		\item One out of three developers comes from a developing country
		
		\textbf{False}, more that one out of three FLOSS developers comes from a developing country.
		\item USA has many more FLOSS developers than the EU, proportionally
		
		\textbf{False}, in USA are not as many FLOSS developers as assumed.
	\end{enumerate}
\end{enumerate}

\end{document}
