\documentclass[11pt]{scrartcl}
\usepackage{atbegshi,picture}
\usepackage{lipsum}

\AtBeginShipout{\AtBeginShipoutUpperLeft{%
  \put(\dimexpr\paperwidth-1cm\relax,-1.5cm){\makebox[0pt][r]{Master on Free Software 2012/2013}}%
}}

\title{\textbf{Developers and motivations}}
\subtitle{Questions about "The Cathedral and the Bazaar"}

\author{Felipe Ortega\\
		Ricardo Grac\'ia Fern\'andez}
\date{\today}
\begin{document}

\maketitle

Revise the content of Eric S. Raymond's essay to answer the following points:
	\begin{enumerate}
		\item In your opinion, which are the 2 most important lessons that we can find in the essay? Provide links and examples to backup your reasoning (1 to 10).\\
		
			\textbf{Answer:} First, in my opinion I think that the first 'rule' is most important:
			\begin{itemize}
				\item 1. Every good work of software starts by scratching a developer's personal itch.
			\end{itemize}
			
			\indent Is most valuable, not only for \textbf{FLOSS} developers but also applies to any field because everyone who wants to do something, has to want to do this thing. This could sound weird and have nosense because it's obvious but you have to be willing to do something to start doing something that interests you, this is the most important not to fall into disuse.
			
			\indent As shown in \emph{Git History}\footnote{http://git-scm.com/book/en/Getting-Started-A-Short-History-of-Git}, in 2005 Linux kernel developers needed a new \emph{DVCS}\footnote{http://en.wikipedia.org/wiki/Distributed\_revision\_control} because of his broke up relation with \emph{BitKeeper}\footnote{http://www.bitkeeper.com/} and then started to develop its own DVCS called Git. Nowadays its the more extended and adopted DVCS worldwide.\\
			
			The second I choose is the eighth one:
			\begin{itemize}
				\item 8. Given a large enough beta-tester and co-developer base, almost every problem will be characterized quickly and the fix obvious to someone.
			\end{itemize}
			
			\indent This rule is very important for a \textbf{FLOSS} developer in every project, you need more eyes not only yours to see how is going your development, users, testers, coders, in summary you need help and have to be capable to admit it and take advantage to make things better and easier.
			
			\indent A sample of spread code could be \emph{Android SDK}\footnote{http://source.android.com/source/downloading.html}. I know, Google only release source code when he wants, but this is not the question, is how code release help your development increases capabilities, gets strong and it's used for more and more people and therefore your beta-tester 'database' increases everyday.
			
		\item Now, find out the 2 most controversial lessons. Again, try to include links and examples to support your comments (1 to 19).

			\textbf{Answer:}
	\end{enumerate}

\end{document}