\documentclass[11pt]{scrartcl}
\usepackage{atbegshi,picture}
\usepackage{lipsum}

\AtBeginShipout{\AtBeginShipoutUpperLeft{%
  \put(\dimexpr\paperwidth-1cm\relax,-1.5cm){\makebox[0pt][r]{Master on Free Software 2012/2013}}%
}}

\title{\textbf{Developers and motivations}}
\subtitle{Transactions on Human-Computer Interaction}

\author{Felipe Ortega\\
		Ricardo Grac\'ia Fern\'andez}
\date{\today}
\begin{document}

\maketitle

\section{Ideas}

	\begin{enumerate}
	
		\item A small fraction of users becomes leaders, who participate in governance by setting and upholding policies, repairing vandalised materials, or mentoring novices.
		\item reading, contributing, collaborating, and leading.
		\item usability and sociability factors.\\
		\begin{tabular}{ | p{6,5cm} | p{6,5cm} |}
			\hline
			Usability & Sociability \\ \hline
			Interesting and relevant content presented in attractive, well-organised layouts & Encouragement by friends, family, respected authorities, advertising \\ \hline
			Frequently updated content with highlighting to encourage return visits & Repeated visibility in incline, print, television and other media \\ \hline
			Support for newcomers through tutorials, animated demos, FAQs, help, mentors, contacts & Understandable and clear norms or policies \\ \hline
			Clear navigation paths so that users have a sense of mastery and control & A sense of belonging based on recognition of familiar people and activities \\ \hline
			Universal usability to support novice/expert, small/large display, slow/fast network, multilingual, and users with disabilities & Charismatic leaders with visionary goals \\ \hline
			Interface design features to support reading, browsing, searching, and sharing & Safety and privacy \\ \hline
		\end{tabular}
					
		\item Usability and sociability factors that may influence contributing.\\
		\begin{tabular}{ | p{6,5cm} | p{6,5cm} |}
			\hline
			Usability & Sociability\\ \hline
			Low threshold interfaces for easily making small contributions, e.g., no login & Support for legitimate peripheral participation so that readers can gradually edge into contributing\\ \hline
			High ceiling interfaces that allow large and frequent contributions & A chance to build their reputation over time while performing satisfying tasks\\ \hline
			Visibility for users’ contributions and frequency of views; aggregated over time & Recognition for the highest quality and quantity of contributions\\ \hline
			Visibility of ratings and comments by community members & Recognition of a person’s specific expertise\\ \hline
			Tools to undo vandalism, limit malicious users, control pornography and libel & Policies and norms for appropriate contributions\\ \hline
		\end{tabular}

		\item Sometimes people shift quickly from contribution to collaboration and back again. For example, an ornithologist contributor to Wikipedia bird articles may be closely collaborating with a group of bird watchers in making sure that an entry about Greater Scaups on the Chesapeake Bay is correct. But she gets distracted by a friend’s email to read an entry about a café in London, whose address is listed as “Upper Road” in Islington, so she corrects it to “Upper Street.” In the first instance, she is involved in a collaboration in which she learns who has a deep knowledge about wildlife on the Bay. In the second instance, she merely contributes the correct address but does not interact with anyone.

		\item Usability and sociability factors that may influence collaborating.\\
		\begin{tabular}{ | p{6,5cm} | p{6,5cm} |}
			\hline
			Usability & Sociability\\ \hline
			Ways to locate relevant and competent individuals to form collaborations & An atmosphere of empathy and trust that promotes belonging to the community and willingness to work within groups to produce something larger\\ \hline
			Tools to collaborate: communicate within groups, schedule projects, assign tasks, share work products, request assistance & Altruism: a desire to support the community, desire to give back, willingness to reciprocate\\ \hline
			Visible recognition and rewards for collaborators, e.g., authorship, citations, links, acknowledgements & The desire to develop a reputation for themselves and their collaborators, their group or community; the need to develop and maintain one’s status within the group\\ \hline
			Ways to resolve differences (e.g., voting), mediate disputes, and deal with unhelpful collaborators & Respect for one’s status within the community\\ \hline
		\end{tabular}

		\item \textbf{Leader}: Promoting participation, mentoring novices, setting and upholding policies.
		
		\item Usability and sociability factors that may influence leadership.\\
		\begin{tabular}{ | p{6,5cm} | p{6,5cm} |}
			\hline
			Usability & Sociability\\ \hline
			Leaders are given higher visibility, and their efforts are highlighted, sometimes with historical narratives, special tributes, or rewards & Leadership is valued and given an honoured position and expected to meet expectations\\ \hline
			Leaders are given special powers, e.g., to promote agendas, expend resources, or limit malicious users & Respect is offered for helping others and dealing with problems\\ \hline
			Mentorship efforts are visibly celebrated, e.g., with comments from mentees & Mentors are cultivated and encouraged\\ \hline
		\end{tabular}

	\end{enumerate}

\section{Exercises}

    Read the paper "The Reader-to-Leader Framework: Motivating Technology-Mediated Social  Participation". Provide 2 additional concrete examples of participation in open online communities that match the different stages suggested in this framework.\\
    This will serve as a starting model to study different motivations of participants in FLOSS development communities.
    
    \subsection{Stackoverflow}
    
	\emph{Stackoverflow} is large community of \emph{Q\&A} about software development. Applying the model exposed in this essay we can distinguish the whole process:
	
	\begin{itemize}
	
		\item \emph{Reader}: A newbie that is there looking for information about specif \emph{question}.
		\item \emph{Contributor}: Registered user that comes back to the community posting a question or answering a comment.
		\item \emph{Collaborator}: Mature registered user that comes frequently to answer questions from another users related his own skills.
		\item \emph{Leader}: User that develops documentation an has a good popularity inside the community.
	\end{itemize}
	
	This is a coding social network that incentive users through experience points an achievements. Each user is free to give points to answers or questions done by a particular user this increases the 'karma'\footnote{http://stackoverflow.com/about}.\\
	Anyone can go from one state to another without nigún problem as seen in the diagram shown above in the essay.	

    \subsection{Codecademy}
    
    \emph{Codeacademy}\footnote{http://www.codecademy.com/} is community to learn programming through some simple tests to increase the difficulty level increases. The whole process can be represented inside this language coding social network:

	\begin{itemize}
	
		\item \emph{Reader}: User that starts programing to learn new language or refresh some knowledge passing test courses.
		\item \emph{Contributor}: Contribute to enhance the tests.
		\item \emph{Collaborator}: User that creates its own tests and tests other to raise a good test to learn an specific language.
		\item \emph{Leader}: User that becomes a test developer and helps others introducing them to test framework, helps in forums and develops \emph{Q\%A} documentation.
	\end{itemize}

	This community as a new user show your achievements day by day retrieving all type of information showed in a human-readable form. Increasing your experience will give you the chance to move from one position to another, learning how it works, using the manuals and creating new ones.\\
	Developing your own tests, look for users to test them, answer the questions and become a \emph{Leader}. You are free to go in every position.
	
	\subsection{Conclusion}
	
	Everyone at any time has the same role depending on need, could be summarised that is a dance of roles where everyone is equal, therefore this type of community work.
	

\begin{thebibliography}{9}
	
	\bibitem{lamport94}
		Transactions on Human-Computer Interaction,\\
		Motivating Technology-Mediated Social Participation.\\
		\emph{Jennifer Preece}.\\
		\emph{Ben Shneiderman}.\\
		http://www.cs.umd.edu/~ben/papers/Jennifer2009Reader.pdf
\end{thebibliography}

\end{document}